An Improved ANS Transaction Template

### 2018-01-27 paper.tex
adding refs

The Joint Comprehensive Plan of Action (JCPOA)\cite{ref} %cite JCPOA agreement
limits the Iranian nuclear program and, in return, lifts many of the economic
sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
limited in its ability to enrich Uranium. This paper presents a model to probe
the enriching ability of various cascade configurations that are related to
JCPOA agreement limits. This analysis was performed using the Cyclus fuel cycle
simulator\cite{ref} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
simulation framework in order to demonstrate that such analysis can be
integrated into a fuel cycle with material flowing among multiple facilities.

The Cyclus fuel cycle simulator is designed to support the dynamic addition
novel facility models into fuel cycles both declared and undeclared facilities.
The CascadeEnrich archetype\cite{ref} was developed to model gas centrifuge
enrichment cascades at a higher fidelity than previous enrichment models,
relying on individual centrifuge and cascade design parameters to build an ideal
cascade configuration instead of integral facility parameters. Once a
CascadeEnrich facility is deployed, it may be asked to participate in the fuel
cycle at a variety of flow rates and enrichments over time, constrained by the
initial design of the cascade.

@@

The present work uses the analytical solution by R\"aetz \cite{ref} of the
differential equation for the gas centrifuge as described in \cite{Glaser2008}.
Centrifuge parameters, such as average gas temperature, rotation speed, height,
feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
efficiency have been chosen to match the cascade design describe in
\cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type
centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.

@@

It can be shown that $\theta_{i}$ can be computed from $\alpha$,
$\beta$ values and the feed assay, $N_{i}$ \cite{ref}:
\begin{eqnarray}
    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
           \dfrac{1}{1 + \beta/R_{i}}}
\end{eqnarray}

@@

Other hypotheses will be explored in the future, such as maintaining the ideal
stage of the cascade through tuning the cut values $\theta_{i}$ of each stage of
the cascade, or maintaining $\alpha*\beta = const$ as described in
\cite{walker2017}.

>>>>

The Joint Comprehensive Plan of Action (JCPOA)\cite{jcpoa} %cite JCPOA agreement
limits the Iranian nuclear program and, in return, lifts many of the economic
sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
limited in its ability to enrich Uranium. This paper presents a model to probe
the enriching ability of various cascade configurations that are related to
JCPOA agreement limits. This analysis was performed using the Cyclus fuel cycle
simulator\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
simulation framework in order to demonstrate that such analysis can be
integrated into a fuel cycle with material flowing among multiple facilities.

The Cyclus fuel cycle simulator is designed to support the dynamic addition
novel facility models into fuel cycles both declared and undeclared facilities.
The CascadeEnrich archetype\cite{mbmore.2018} was developed to model gas centrifuge
enrichment cascades at a higher fidelity than previous enrichment models,
relying on individual centrifuge and cascade design parameters to build an ideal
cascade configuration instead of integral facility parameters. Once a
CascadeEnrich facility is deployed, it may be asked to participate in the fuel
cycle at a variety of flow rates and enrichments over time, constrained by the
initial design of the cascade.

@@

The present work uses the analytical solution by R\"aetz \cite{raetz.phd} of the
differential equation for the gas centrifuge as described in \cite{glaser.2008}.
Centrifuge parameters, such as average gas temperature, rotation speed, height,
feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
efficiency have been chosen to match the cascade design describe in
\cite{glaser.2008} and \cite{walker.2017}. These parameters for a P1-type
centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.

@@

It can be shown that $\theta_{i}$ can be computed from $\alpha$,
$\beta$ values and the feed assay, $N_{i}$:
\begin{eqnarray}
    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
           \dfrac{1}{1 + \beta/R_{i}}}
\end{eqnarray}

@@

Other hypotheses will be explored in the future, such as maintaining the ideal
stage of the cascade through tuning the cut values $\theta_{i}$ of each stage of
the cascade, or maintaining $\alpha*\beta = const$ as described in
\cite{walker.2017}.
